\documentclass[a4paper,overlapped]{res}
\usepackage[default]{droidserif}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{url}
\setlist[itemize]{leftmargin=*}


\begin{document}
\name{Ashutosh Rishi Ranjan}


\begin{resume}
  \moveleft.5\hoffset\centerline{1/42 Athol Street, Moonee Ponds, VIC 3039, Australia}
  \moveleft.5\hoffset\centerline{+61 452 482 036}
  \moveleft.5\hoffset\centerline{ashutoshrishi92@gmail.com}

  \section{Education}  
  \textbf{University of Melbourne} \hfill \textit{Graduated in July 2016} \\
  \textbf{M.Sc. Computer Science }
  \begin{itemize} \itemsep -2pt
  \item[--] \textbf{Weighted Average}: 79.5
  \item[--] Relevant courses: Declarative Programming, Programming Language
    Implementation, \\ Web Search \& Text Analysis, Distributed Systems \&
    Distributed Algorithms, \\
    Cluster \& Cloud Computing, Parallel \& Multi-core Computing.
  \end{itemize}

  \textbf{Symbiosis University, Pune, India} \hfill \textit{Graduated 2014} \\
  \textbf{B.Tech. Computer Science }


  \section{Coursework Projects}
  
  \textbf{Masters Research Project on the Wybe Compiler} \hfill
  \textit{2015 to 2016}\\
  \textbf{University of Melbourne}
  \begin{itemize}
  \item Worked on a compiler for a new multi-paradigm language, \textit{Wybe},
    with a new Logic \\ Programming based Intermediate Representation
    (\textit{LPVM}) and a LLVM target.
  \item Wrote the back-end of the Compiler in Haskell.
  \item Researched and implemented various techniques to create an incremental
    and \\work-saving compilation process.
  \item Compiler includes a modern GNU Make-like build system.
  \item Thesis link: \url{https://github.com/ashutoshrishi/wybe-thesis}
  \end{itemize}

  \textbf{Compiler for a Toy Language in OCaml} \hfill \textit{Semester 1,
    2016}\\
  \textbf{Programming Language Implementation, UniMelb}
  \begin{itemize}
  \item Implemented a complete compiler for a toy language in OCaml as part of
    a semester\\ long project.
  \item Developed a basic \textit{diff} based testing framework in OCaml for
    continuous testing of \\ the compiler outputs as extra work:
    \url{https://github.com/ashutoshrishi/difftest}
  \item Project link: \url{https://bitbucket.org/pli2016/beanc}
  \end{itemize}
  

  \textbf{Twitter Analysis REST Service over an Open Stack IAAS,} 
  \hfill \textit{Semester 1, 2015}\\
  \textbf{Cluster and Cloud Computing, UniMelb}
  \begin{itemize}
  \item Wrote a Python client to harvest geo-located tweets around SF into a
    CouchDB \\
    instance. The client ran as a daemon parallely from two different servers.
  \item Wrote a Python application to perform several different natural
    language analyses on \\ the stored data using CouchDB Map-Reduce
    views, and served their results through a REST API.
  \item Set up a NGINX web server on a Linux based instance to host a website
    presenting this data \\ through client-side graphs and heat maps rendered
    with Javascript.
  \item We built our own orchestration tool using Bash scripts and rsync,
    imitating \textit{Ansible}.
  \item Project Link: \url{https://bitbucket.org/cccteam6/cctwittersearch}
  \end{itemize}
  

  \section{Experience}

  \textbf{Web Developer,} \hfill \textit{Contract basis, 2015}\\
  \textbf{Melbourne Web Co.}
  \begin{itemize}
  \item Worked independently and within a team environment on multiple web 
    development projects using the Wordpress platform for local Australian businesses.
  \item Developed custom Wordpress plugins in PHP for a few jobs.  
  \end{itemize}
  
  \textbf{Intern, Assistant to Project Manager,}  \hfill \textit{June 2013}\\
  \textbf{Bahwan Cybertek, Oman}
  \begin{itemize}
  \item Modelled an implementation of an IBM Maximo Asset management 
    solution for a client. 
  \item Created a concept design for a responsive website for Bahwan Cybertek 
    for the IT team. 
  \end{itemize}

  \textbf{IT Intern,} \hfill \textit{January to May, 2013}\\
  \textbf{HELLA India}
  \begin{itemize}
  \item Developed a complete new in-house Inventory Management System on a PHP
    back-end for the team responsible of maintaining the local HELLA electronics stock.
  \item Configured and Deployed an Employee Training Portal using the
    Moodle framework.
  \item Recorded usage videos and documentation to help other teams in their
    adoption of the portal.
  \end{itemize}


  \section{Code}
  \begin{tabular}{l l}
    Github:    & \url{https://github.com/ashutoshrishi} \\
    Bitbucket: & \url{https://bitbucket.org/ashutoshrishi/profile/teams}
  \end{tabular}
  

  \section{Technical Skills} 
  \textbf{Languages:} \\ 
  \begin{tabular}{l l}
    Current Projects: & Haskell, Elm, Javascript (ES6+5) \\ 
    Worked With: & Python, OCaml, Java, C, PHP, C++ \\
  \end{tabular}

  \textbf{Programming language implementation:} Compiler Design using LLVM \\
  \textbf{Web Development and Design:}
  \begin{itemize}
  \item Programmed back-ends in Javascript, Haskell, Python, and PHP.
  \item Experience with designing and using REST APIs.
  \item JS Toolkit: ReactJS, Express, JQuery among
    others.
  \item Front-end development with responsive design and a focus on good UI/UX.
  \end{itemize}
  \textbf{Platforms:}
  \begin{itemize}
  \item Experienced with Unix/Linux; Configuring NGINX and Apache web servers on
    Linux.
  \item Worked on projects built upon Open Stack.
  \end{itemize}


  
  % \section{Extra Curricular Activities}  

  % \textbf{Co-Head, Student Technical Committee}   \hfill \textit{2012} \\
  % \textit{Symbiosis Institute of Technology, Pune, India}
  % \begin{itemize}
  % \item Developed the annual college festival website and registration back-end
  %   in PHP.
  % \item Managed the team's finances and techinical logistics, while collaborating 
  %   with other teams.
  % \item Created designs for the brochures and provided other design related guidance to
  %   other teams.
  % \end{itemize}


  \section{Other Personal Details}
  \begin{tabular}{l l}
    % \textbf{Nationality:} & Indian \\
    \textbf{Current Visa:} & Australian Graduate Work Visa \\
    \textbf{Languages:} & English (fluent), Hindi \\
    \textbf{Date of Birth: } & 26/09/1992 (Age: 23) \\ 
    \textbf{Hobbies:} & Cycling, Muay Thai \\
  \end{tabular}

  % \section{Referees}
  % Available Upon Request.
  
\end{resume}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
